Misexpression of germline programs with loss of the X-linked intellectual disability factor KDM5C

### 2024-04-23 submission/manuscript.Rmd
fix figure legend typo

\begin{figure}
  \centering 
  \includegraphics{../submission/compiled_figs/EpiLCs_too.pdf}
  \caption[\textit{Kdm5c}-KO epiblast-like cells express master regulators of germline identity ]{\textbf{\textit{Kdm5c}-KO epiblast-like cells express master regulators of germline identity A.} Top - Diagram of \textit{in vivo} differentiation of emrbyonic stem cells (ESCs) of the inner cell mass into epiblast stem cells. Middle - \textit{in vitro} differentiation of ESCs into epiblast-like cells (EpiLCs). Bottom - representative images of wild-type (WT) and \textit{Kdm5c}-KO ESC to EpiLC differentiation. Brightfield images taken at 20X. \textbf{B.} No significant difference in primed pluripotency maker expression in wild-type versus \textit{Kdm5c}-KO EpiLCs. Welch's t-test, expression in transcripts per million (TPM). \textbf{C.} Number of tissue-enriched differentially expressed genes (DEGs). * p<0.05, ** p<0.01, *** p<0.001, Fisher's exact test. \textbf{D.} Average bigwigs of an example germline gene, \textit{Cyct} that is dysregulated \textit{Kdm5c}-KO EpiLCs. \textbf{E.} Upset plot displaying the overlap of germline DEGs expressed in \textit{Kdm5c}-KO mutant EpiLC, amygdala (AMY), and hippocampus (HIP) RNA-seq datasets. \textbf{F.} enrichPlot comparing enriched gene ontoogies for \textit{Kdm5c}-KO EpiLCs, amygdala, and hippocampus germline DEGs. \textbf{G.} Top - Example germline identity DEGs unique to EpiLCs, p-values for Welch's t-test. Bottom - Average bigwigs of \textit{Dazl} and \textit{Stra8} expression in wild-type and \textit{Kdm5c}-KO EpiLCs \textbf{H.} Immunocytochemistry of DAZL in male wild-type (WT) and \textit{Kdm5c}-KO (5CKO) EpiLCs. Percentage of DAZL-positive cells normalized to DAPI, p-value for Welch's t-test}
  \label{figurelabel}
\end{figure}

>>>>

\begin{figure}
  \centering 
  \includegraphics{../submission/compiled_figs/EpiLCs_too.pdf}
  \caption[\textit{Kdm5c}-KO epiblast-like cells express master regulators of germline identity ]{\textbf{\textit{Kdm5c}-KO epiblast-like cells express master regulators of germline identity A.} Top - Diagram of \textit{in vivo} differentiation of embryonic stem cells (ESCs) of the inner cell mass into epiblast stem cells. Middle - \textit{in vitro} differentiation of ESCs into epiblast-like cells (EpiLCs). Bottom - representative images of wild-type (WT) and \textit{Kdm5c}-KO ESC to EpiLC differentiation. Brightfield images taken at 20X. \textbf{B.} No significant difference in primed pluripotency maker expression in wild-type versus \textit{Kdm5c}-KO EpiLCs. Welch's t-test, expression in transcripts per million (TPM). \textbf{C.} Number of tissue-enriched differentially expressed genes (DEGs). * p<0.05, ** p<0.01, *** p<0.001, Fisher's exact test. \textbf{D.} Average bigwigs of an example germline gene, \textit{Cyct} that is dysregulated \textit{Kdm5c}-KO EpiLCs. \textbf{E.} Upset plot displaying the overlap of germline DEGs expressed in \textit{Kdm5c}-KO mutant EpiLC, amygdala (AMY), and hippocampus (HIP) RNA-seq datasets. \textbf{F.} enrichPlot comparing enriched gene ontoogies for \textit{Kdm5c}-KO EpiLCs, amygdala, and hippocampus germline DEGs. \textbf{G.} Top - Example germline identity DEGs unique to EpiLCs, p-values for Welch's t-test. Bottom - Average bigwigs of \textit{Dazl} and \textit{Stra8} expression in wild-type and \textit{Kdm5c}-KO EpiLCs \textbf{H.} Immunocytochemistry of DAZL in male wild-type (WT) and \textit{Kdm5c}-KO (5CKO) EpiLCs. Percentage of DAZL-positive cells normalized to DAPI, p-value for Welch's t-test}
  \label{figurelabel}
\end{figure}
